---
title: "Chap1-8, Ruppert"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapters 1 - 8 cover basic algebra and statistics


### Chap 1: Introduction Omitted

### Chap 2: Returns
Instead of using existing quotation data, I use **quantmod** and **tidyquant** to access yahoo api.
```{r eval=FALSE}
install.packages{"quantmod"}
install.packages{"tidyquant"}
```
*If Console doesn't work, try Packages - Install button.*



```{r message=FALSE, warning=FALSE}
library(tidyquant)
getSymbols("AMZN", from = '2016-01-01', to = '2020-12-31', warnings = FALSE, auto.assign = TRUE)
head(AMZN)
```
```{r }
class(AMZN)
chart_Series(AMZN)
```
To specify an asset universe, use a list:
```{r}
tick_basket = c("AAPL", "AMZN", "NFLX", "K")
getSymbols(tick_basket, from = '2016-01-01', to = '2020-12-31')
```
The locally imported csv:
```{r}
setwd("~/Ruppert/datasets")
data = read.csv("Stock_bond.csv", header = TRUE)
```
```{r}
names(data)
attach(data)
par(mfrow = c(1, 2)) #setting form of graphics: 1*2 horizontal display
plot(GM_AC)
plot(F_AC)
```

```{r}
dim(data) #number of obs by number of assets. Returns a vector
nAss = dim(data)[1]
#Simple Return Calc
GM_Ret = GM_AC[-1]/GM_AC[-nAss] - 1 #-1: all but first. -nAss: all but last. In total: vector element division. Price: old to new
F_Ret = F_AC[-1]/F_AC[-nAss] - 1
par(mfrow = c(1, 1)) #Pivot 
plot(GM_Ret, F_Ret)
```

Simulate prices

```{r}
niter = 1e5
below = rep(0, niter) #arange
set.seed(2009)
for (i in 1:niter)
{
  r = rnorm(45, mean = 0.05/253, #a set normal random variable
            sd = 0.23/sqrt(253))
  logPrice = log(1e6)+cumsum(r) #cumulative log price for each
   minlogP = min(logPrice)
  below[i] = as.numeric(minlogP < log(9500000))
}  
mean(below)
```
In this case, i's value does not enter the for loop at all. It is only a numeration of simulations. 
rnorm generates 45 values then cumsum. It simulates the next 45 periods for one instance. Do this 1e5 times.
This snippet is a lognormal price development.
---

Geometric Random Walk.
```{r}
set.seed(2012)
n = 253
par(mfrow = c(3,3))
for (i in (1:9))
{ 
  logr = rnorm(n, 0.05/253, 0.2/sqrt(253)) #specified normal, i.i.d.
  price = c(120, 120*exp(cumsum(logr))) # 120: starting price, then ending prices at each day.
  plot(price, type = 'b')
}  
```

### Chap 3: Fixed Income
**Introducing user defined functions.**

1. Compute bond price
```{r}
bondprice = function(c, T, r, par)
{
  # c coupon payment, semiannual
  # T time to maturity
  # r vector of yields to maturity
  # par face value
  bv = c/r + (par - c/r)*(1+r)^(-2*T)
  bv
}
```
Pay attention to the formalism of function in R (similar to MATLAB).
Below is the formalism. Note the customized setup.
$$ P = \sum_{t=1}^{2T} \frac{C}{(1+r)^6}+\frac{PAR}{(1+r)^{2T}} = \frac{C}{r}+\{PAR-\frac{C}{r}\}(1+r)^{-2T} $$

After some reshuffling, the formula is barely intelligible.
2. Yield to Maturity
essentially IRR. 
```{r}
price =1200
C =40
T =30
par = 1000

r= seq(0.02, 0.05, length = 300)
value = bondprice(C, T, r, par)
ytm = spline(value, r, xout = price)

plot(r, value, xlab = 'YTM', ylab = 'Bond Price',
     type ='l', main = 'par = 1000, c = 40, 
     T = 30', lwd = 2)
abline(h = 1200)
abline(v = ytm)
```
The function does not need to take r as a vector. This arrangement is only for graphing, i.e. from a range of r to a range of value.
** non linear root finder**
for a function. ** uniroot **
```{r}
uniroot(function(r) r^2 - .5, c(0.7, 0.8))
```

```{r}
uniroot(function(r) 40/r + (1000 - 40/r)*(1+r)^(-2*30) - 1200, c(0.02, 0.05))
```
Find solution by formulating an equation with one unknown parameter.
```{r}
library("fEcofin")
mk.maturity = fEcofin::mk.maturity
mk.zero2 = fEcofin::mk.zero2
plot(mk.maturity[, 1], mk.zero2[5, 2:56], type = "l", xlab = "maturity", ylab = "yield")
lines(mk.maturity[, 1], mk.zero2[6, 2:56], lty = 2, type = "l")
lines(mk.maturity[, 1], mk.zero2[7, 2:56], lty = 3, type = "l")
lines(mk.maturity[, 1], mk.zero2[8, 2:56], lty = 4, type = "l")
legend('bottomright', c("1985-12-01", "1986-01-01", "1986-02-01", "1986-03-01"), lty = 1:4)
```
Directly query package data: fEcofin::mk.maturity. 
Do not change directory!
```{r}
intForward = mk.maturity[, 1] * mk.zero2[6, 2:56]
xout = seq(0, 20, length = 200)
z1 = spline(mk.maturity[, 1], intForward, xout = xout) #x must enter y. xout: points on the span to fill, given x to get y
forward = diff(z1$y) / diff(z1$x)
T_grid = (xout[-1] + xout[-200]) / 2
plot(T_grid, forward, type = "l", lwd = 2, ylim = c(0.06, 0.11))

```
Spline is a non-parametric model.
forward: is not really a continuous function but a piece-wise cumulative product.

3. Spot Rate: nothing
4. Term Structure: See above
5.Duration Convexity Match: Nothing.
Duration, Convexity can be crudely applied in bond hedging. It is equivalent to solving linear equations.

### Chap 4: Exploratory Data Analysis

























